hormones

### 2020-02-03 analysis/07_hormones.Rmd
now with dense figures

  aov_all = data.frame()
  for(i in alllevels3){
    df <- hormones %>% filter(hormone == myhormone,
                            treatment == i) %>% droplevels()
    aovtable <- apa.aov.table(aov(plasma_conc ~ sex, data  = df))
    aovtable <- as.data.frame(aovtable$table_body)
    totaldf <- aovtable[3, 3]
    aovtable$df <- paste(aovtable$df, ", " , totaldf, sep = "")
    aovtable$ANOVA <- mydescirption
    aovtable$stages <- paste(i)
    aovtable$p <- as.numeric(as.character(aovtable$p))
    aov_all <- rbind(aov_all,aovtable)
  }

@@

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4), labels = c("c","d"), label_size = 8 )

plot_grid(p12, p34, nrow = 2, rel_heights = c(0.6,0.4))
```

@@

plot_grid(p12, p34, nrow = 2, rel_heights = c(0.5,0.5))
```

@@

```{r supplefig, fig.height=8}
plot_grid(p1, p2, p3 + labs(y = NULL), p4, p5, p6, p7 + labs(y = NULL), p8, 
          p9, p10, p11 + labs(y = NULL), p12, nrow = 3, rel_widths =   c(0.175,0.4,0.35,0.25), align = "hv",
          label_size = 8, labels = c("a", " ", " " , " ",
                                     "b", " ", " " , " ",
                                     "c", " ", " " , " "))

@@

twos <- plot_grid(a2,b2,c2, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

plot_grid(ones,twos, nrow = 2)
```

>>>>

  aov_all = data.frame()
  for(i in alllevels){
    df <- hormones %>% filter(hormone == myhormone,
                            treatment == i) %>% droplevels()
    aovtable <- apa.aov.table(aov(plasma_conc ~ sex, data  = df))
    aovtable <- as.data.frame(aovtable$table_body)
    totaldf <- aovtable[3, 3]
    aovtable$df <- paste(aovtable$df, ", " , totaldf, sep = "")
    aovtable$ANOVA <- mydescirption
    aovtable$stages <- paste(i)
    aovtable$p <- as.numeric(as.character(aovtable$p))
    aov_all <- rbind(aov_all,aovtable)
  }

@@

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4), labels = c("c","d"), label_size = 8 )
p34

allcortplots <- plot_grid(p12, p34, nrow = 2, rel_heights = c(0.6,0.4))
allcortplots
```

@@

allprolactinplots <- plot_grid(p12, p34, nrow = 2, rel_heights = c(0.5,0.5))
allprolactinplots
```

## figure 2

```{r figure2, fig.width=7, fig.height=7}

plot_grid(allprolactinplots, allcortplots, nrow = 2)
```

@@

```{r supplefig, fig.height=8}
sexsteroids <- plot_grid(p1, p2, p3 + labs(y = NULL), p4, p5, p6, p7 + labs(y = NULL), p8, 
          p9, p10, p11 + labs(y = NULL), p12, nrow = 3, rel_widths =   c(0.175,0.4,0.35,0.25), align = "hv",
          label_size = 8, labels = c("a", " ", " " , " ",
                                     "b", " ", " " , " ",
                                     "c", " ", " " , " "))
sexsteroids
```

@@

twos <- plot_grid(a2 + theme(title = element_blank()),b2,c2, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

plot_grid(ones,twos, nrow = 2)

twos
```

```{r figure3, fig.height=8, fig.width=7}

plot_grid(twos,sexsteroids, nrow = 2, rel_heights = c(0.25,0.75), align = "hv")
```
